---
title: "Analysis of Comita's Seedling Data"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r, warning=FALSE,message=FALSE, echo=FALSE}
library(ggplot2)
library(tidyverse)
library(magrittr)
```


```{r, warning=FALSE,message=FALSE, echo=FALSE}
source("C:/Users/ahanb/OneDrive/Documents/RecruitmentToyModel/RecruitmentToyModel/comita_seedling_analysis/LOAD_seedling_data.R")
source("C:/Users/ahanb/OneDrive/Documents/RecruitmentToyModel/RecruitmentToyModel/comita_seedling_analysis/MUNGE_seedling_dyn_data_Johnson.R")
```


**Goal**: To derive a relationship between light in the seedling layer and the fraction of the seedling pool that transitions to the 1 cm size class.



###Step 1: Convert shade index to relative irradiance (RI)


The comita data gives a shade index for each 5X5 m quadrat over each census interval. See more about this shade index on Rick Condit's [website](http://richardcondit.org/data/canopy/bciCanopyReport.php). I replicated the method used in Ruger et al. 2009 to convert the indices to RI values. I assumed the 0, 5, 25, 50, 75, 95, and 100th percentiles of the shade indices match the same percentiles of the Wirth et al. 2001 RI data and did a regression through those points.

I compared linear, quadratic, and cubic regressions. The cubic regression was the best fit and is shown as the green line in the graph below.
```{r, echo=FALSE}
library(ggplot2)
ggplot(data = l_shd_data, mapping = aes(x = shd, y = lnRI)) +
  geom_point() +
  #geom_line(mapping = aes(x = shd, y = predict(l_shd_m_quad, newdata = l_shd_data))) +
  #geom_line(mapping = aes(x = shd, y = predict(l_shd_m, newdata = l_shd_data))) +
  geom_line(mapping = aes(x = shd, y = predict(l_shd_m_3, newdata = l_shd_data)), color = "green1")+
  xlab("shade index") +
  ylab("ln(RI)") +
  labs(title = "Converting shade index to relative irradiance")+
  theme(plot.title = element_text(vjust = 3, size = 15))
```



###Step 2: Convert relative irradiance to the daily mean PFD (umol m^-2^ s^-1^) in each quadrat in each census interval

1) The source data I used was BCI top of canopy daily irradiance in MJm2 per day. 
2) I converted that to the daily mean PFD (umol m^-2^ s^-1^). My PFD variable is the average of all the instantaneous PFD values you would get over the course of a day. I then multiplied that number by the RI values in each quadrat over each census interval to get the mean daily PFD at 0.5 m above the ground in each 5x5 m quadrat during each census interval.

Assumption: 12 hours of daylight per day. 

###Step 3: Fitting a model with PFD as the predictor and seedling transition rate as the response 
```{r}

mod3 <- lm(log(daily_t_rate + 1) ~ log(PFD), data = seed_dyn_c)
summary(mod3)
```
**Conclusion**: There is a positive relationship between the natural log of the mean daily PFD and natural log of the daily seedling transition rate. (p = 0.0261).

Despite the fact that the relationship is statistically significant, you can't really tell by looking at a scatter plot (see below). 
```{r}
ggplot(data = seed_dyn_c, mapping = aes(x = log(PFD), y = log(daily_t_rate+1)))+
  geom_point()+
  #geom_line(mapping = aes(y =(exp(predict(mod3, newdata = seed_dyn_c))-1), x = log(PFD)))
  labs(title = "The relationship between PFD and seedling transition rate")+
  xlab("ln(PFD)")+
  ylab("ln(daily seedling transition rate + 1)")

```



###Step 4: Viewing the modeled relationship. 

Here is what the modeled relationship looks like between PFD in the seedling layer and the predicted daily seedling transition rate.
```{r}
plot(x = seed_dyn_c$PFD, y = exp(predict(mod3, newdata = seed_dyn_c))-1, xlab = "PFD", ylab = "Daily Seedling Transition Rate")
```


