---
title: "Log of Work on Toy Model"
output: html_notebook
---



```{r}
plot(cars)
```


2/19/2018

I tried to rework my benchmarking scripts to make them more interpretable and reproducible, but this attempt failed because it would be a week long process. For now I'll have to rely on the reports, presentations, and Rmarkdown word docs that I've created.

2/20/2018

I noticed that the recruitment rates (into the 1 cm size class) that I calculated from the seedling dynamics data that Dan Johnson are two order of magnitude lower than the recruitment rates (into the 1 cm size class) I calculated from the bci forest dynamics plot data.

I tried to use the publicacly available data to reconcile this and use it as another data point. The most I can deduce from that public seedling dynamics data is that 

2/25/2018

The R squared values are way too small. Need to run this as a multivariate glm perhaps? 

Talk to Lara about this again. Perhaps there is a way to use the Ruger approach and relate whats coming in to the 1 cm size class to light and the density of seedlings in each quadrat? I could theoretically do this for the 2005 and 2010 censuses. 


If go ahead with Lara's idea:

1. read up on multivariate glm for standardizing variables.
2. transform data to recruit or no recruit.
2. run a multivariate glm with early and late.


2/27/2018

Talk with Lara. Check the feasibility of my idea to join the dynamics data with the 1cm size class data.

1. Check variation over years of seedling density in the 5x5 plot
2. Check variation of 5 X 5 plots within a 20 meter plot
3. Check how many 5x5 plots there are within each 20 meter plot
4. Check if I can line up the 5x5 meter plots with the 20 m plots.



The summary stats of standard errors for interannual variation in number of seedlings per 5X5 quadrat

Interannual Means
Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  1.000   1.000   1.857   2.516   3.143  31.143 


Internnual Standard Deviations
Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.5774  0.8787  1.1547 22.5494

Standard Errors
Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.0000  0.2608  0.3600  0.4899  8.5229 



Variation within a 20X20 plot

Mean

Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  1.000   2.029   2.512   2.656   3.082  11.931
  

Sd
Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  0.000   1.277   1.753   1.919   2.325  13.107 

Se
Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.1635  0.2175  0.2374  0.2842  1.3042 



Number of 5x5 plots in each 20x20 plot

Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
   1.00   10.00   12.00   12.01   14.00   16.00




Yes, I can line the plots up.


Look at the 20 X 20 m death rates, death rate over the same interval. 


3/15/2018

Today I am going back to second iteration of the toy model, based off of Kobe's work to:

1. Use the light dependent mortality functions that he found to best fit the species
2. Understand what parameters in those functions I can tweak to get desired recruitment rates at various light levels. Name those parameters.
3. Tweak those parameters to get recruitment rates line up with what Ruger finds.


Get light dependent recruitment rates for each PFT from Ruger
Parameterize Kobe's functional form to match Ruger


Assumptions of the recruitment function
1) Early PFT seedlings have a basal diameter of 1.3 cm, late PFTs have a basal diameter of 1.46 cm
2) Early PFT seedling contain 162.2 grams of carbon, Late PFTs contain 175.35 grams of carbon.
3) 


Note about units of light in recruitment function:

Kobe's light dependent relative growth rate function requires light to be in units of relative irradiance. In order to use his parameters I have to preserve that his functional form. We can still feed the function absolute light, but I will have to make the function convert absolute light to the corresponding relative irradiance at Kobe's field site in La Selva. 


Determining benchmarks and how to initialize:

I calculated there to be about 650 seedlings seedlings per hectare on bci. (above 20 cm height and less than 1 cm dbh).

There is also about 30 to 35 g of carbon in each seedling depending on PFT 


```{r}
650*35
```

Thus, there should be approx. 22,750 g of carbon per ha in the seedling pool at any given time for a plot like bci.

The average number of woody tree recruits per ha per year on bci is 110 individuals

*Therefore, the average fraction of the seedling pool that transitions at 2 percent light should be around 



3/17/2018
Goal:

Create an Rmarkdown that shows model output and what the different parameterizations are



Next Steps:

1. Find a way to stop there being so much carbon in the seedbank and seedling pool. First consider changing existing seed decay and seedling mortality parameters, then consider adding in a density dependence according to the last paper that Lara sent me.


2. Make the recruitment graphs only graph a running mean of daily recruitment rates. 














